
---
title: Example and use case
author: Nicolas Rochat
editor_options: 
  chunk_output_type: console
---





## A classic scale

For this use case we will use the data from Rochat et al. (2025). The scale is an
inference measure scale for children between 6 and 10 years old and is considered
as a factor of comprehension.

We start by importing the data and defining the items for the analysis.

```{r}
#| message: false
#| warning: false

library(psychometRics)
library(dplyr)
library(kableExtra)

data("inference")
items <- c(paste0("item_0",3:9),"item_10")
head(inference)

```

Now we can run the functions to evaluate classical test theory: frequency of answers, item difficulty, item discrimination, and Cronbach's alpha.

```{r}
scan.freq(data = inference, items = items)
scan.diff(data = inference, items = items)
scan.disc(data = inference, items = items)
scan.alpha(data = inference, items = items)
```

All those functions can be executed in a single command.


```{r}
eval1 = eval.ctt(inference, items)
eval1
```


A detection function to identify problematic items can also be run. The objective of the function is to provide assistance in detecting weak items.
It returns a list of items and the reason for each flag. When using the `summary` method, a kable table highlighting the flagged values is produced.

```{r}
d.eval1 <- detect.eval.ctt.warn(eval1)
d.eval1
```



By default, the detection method uses standard values, but you can increase the requirements to ensure higher quality.

```{r}

d.eval1.alt <- detect.eval.ctt.warn(eval1,threshold.disc = 0.35)

```
```{r}
#| echo: true 
#| eval: false

summary(d.eval1.alt)

```
```{r}
#| echo: false 
d.eval1.alt
d.eval1.alt$table %>% kbl(escape = FALSE) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```




## The case of Multiple Choice Questions


Some test evaluations often include MCQs. MCQs are generally constituted by a correct answer (called the key) and incorrect answers (distractors).
Those alternatives can be inspected to detect issues.



```{r}
item.1 <- c(rep("A", 15), rep("B", 10), rep("C", 15))
item.2 <- c(rep("A", 10), rep("B", 15), rep("C", 15))
item.3 <- c(rep("A", 5), rep("B", 15), rep("C", 20))
item.4 <- c(rep("A", 3), rep("B", 19), rep("C", 18))
item.5 <- c(rep("A", 11), rep("B", 13), rep("C", 16))

dat.response <- data.frame(
  item.1 = item.1,
  item.2 = item.2,
  item.3 = item.3,
  item.4 = item.4,
  item.5 = item.5
)

key <- c("A","B","C","A","B")

dat.score <- data.frame()
for (i in 1:nrow(dat.response)){
  tmp <- dat.response[i,] == key
  dat.score <- rbind(dat.score, as.data.frame(tmp))
}

dat.score <- as.data.frame(sapply(dat.score,as.numeric))
```


```{r}
rar <- scan.rar(dat.score,items = paste0("item.",1:5),data.response = dat.response,items.rar = paste0("item.",1:5))
rar

d.rar <- detect.rar.warning(rar, keys = key)
d.rar
```



```{r}
#| echo: true 
#| eval: false

summary(d.eval1.alt)

```
```{r}
#| echo: false 
d.rar
object = d.rar

  tmp <- object$data_rar %>%  mutate_if(is.numeric, round, digits = 3 )
  tmp[object$aggregate.warning] <- cell_spec(tmp[object$aggregate.warning],  background = "red")

  ambigus.distractor <- rowSums(object$ambigus.distractor)
  weak.key <-  rowSums(object$weak.key)
   if(!is.null(object$uncredible.distractor)) {
    uncredible.distractor <- rowSums(object$uncredible.distractor)
  } else {
    uncredible.distractor <- NA
  }

  tmp2 <- data.frame(ambigus.distractor,weak.key,uncredible.distractor)
  tmp2[tmp2>0 & !is.na(tmp2)] <- cell_spec(tmp2[tmp2>0 & !is.na(tmp2)],  background = "red")

 object$data_info |> cbind(tmp,tmp2) %>%
    kbl( booktabs = T, digits = 3, longtable = T,escape = F) %>%
    kable_paper("striped", full_width = F)
```






## References

Rochat, N., Lima, L., & Bressoux, P. (2025). *The Riddle Knowledge Inference Test (R-Kit)*. Journal of Psychoeducational Assessment, 43(3), 328-343.
